---
title: "Data Products week 2"
author: "Arvind Kumar"
date: "August 30, 2019"
output: html_document
  ---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## World Cities Map
The map shows a map of the world cities. The data was taken from https://simplemaps.com/data/world-cities
Introduction
The goal of this assignment is to create a web page using R Markdown that features a map created with Leaflet. The webpage should be hosted on either Github Pages, RPubs, or NeoCities. The webpage must also contain the date when the document was created.
```{r 1}
library(knitr)
library(leaflet)
library(dplyr)
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lat=28.6129, lng=77.2295, popup="India Gate, Delhi") %>%
  addMarkers(lat=28.5244,lng=77.1855, popup="Qutb Minar, Delhi") %>%
  addMarkers(lat=28.6562,lng=77.2410, popup="Red Fort, Delhi") %>%
  addMarkers(lat=28.5933,lng=77.2507, popup="Humayun's Tomb, Delhi") %>%
  addMarkers(lat=28.6264,lng=77.2089, popup="Gurudwara Bangla Sahib, Delhi") %>%
  addMarkers(lat=28.6127,lng=77.2773, popup="Akshardham, Delhi") #%>%
  #setView (lat=28.6129, lng=77.2295, zoom=16) 
  m  # Print the map
```

